Physcraper: A Python package for continually updated phylogenetic trees using the Open Tree of Life

### 2021-04-20 sources/bmc_template_submission/bmc_article.tex
fixing cites

Physcraper is implemented with Python and can also be run on the command line.
It currently consists of 12 modules.
%% , classes, methods and functions.%%
For testing and improving Python code’s syntax quality of the Phsycraper code, we
used the Pylint software following instructions from their website \citep{pylintWeb}
 and manual \citep{pylintManual}, with a "".pylintrc" configuration file.

>>>>

Physcraper is implemented with Python and can also be run on the command line.
It currently consists of 12 modules.
%% , classes, methods and functions.%%
For testing and improving Python code’s syntax quality of the Phsycraper code, we
used the Pylint software following instructions from their website \cite{pylintWeb}
 and manual \cite{pylintManual}, with a ".pylintrc" configuration file.
